Paper

### 2019-11-05 Paper.Rmd

```{r labelsPNP, echo=F, message=F, include=T}
cache.dir = paste(data, 'Analysis/5e6_arms', sep='/') # QC'd

@@

chr.lengths = BarrettsProgressionRisk:::chrInfo(prefix = '') %>% dplyr::filter(chr %in% c(1:22)) %>%
  dplyr::mutate(chrom = factor(sub('chr','', chrom), levels=c(1:22), ordered=T))

@@

mp$performance[,c('n.Coef','25%','50%','75%', '100%')] %>% kable(caption='Number of features stable in >=n% of folds') %>% kable_styling()
```

>>>>

```{r labelsPNP, echo=F, message=F, include=T}
cache.dir = paste(data, 'Analysis/models_5e6/50kb', sep='/') # QC'd

@@

chr.lengths = BarrettsProgressionRisk:::chrInfo() %>% dplyr::filter(chr %in% c(1:22)) %>%
  dplyr::mutate(chrom = factor(sub('chr','', chrom), levels=c(1:22), ordered=T))

@@

mp$performance[,c('n.Coef','25%','50%','75%', '100%')] %>% kable(caption='Number of features stable in >=n% of folds') %>% kable_styling(full_width = F)
```
